An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2017-03-20 uai2017/paper.tex
update uai2017 paper: gaussian mixture experiment results

% Daniel: moving this here so figures don't overflow to next pages. We can tune
% the positioning if needed.
\begin{figure*}[t]
    \centering
    \includegraphics[width=0.9\linewidth]{posterior_of_gaussian.png}
    \caption{
    The log posterior contours and scatter plots of sampled $\theta$ values
    using different methods. 
    }
    \label{fig:gauss_mix_1}
\end{figure*}
\begin{figure*}[t]
    \centering
    \includegraphics[width=0.9\linewidth]{minibatch_size_gaussian.png}
    \caption{
    Minibatch sizes used in Section~\ref{ssec:gaussians}'s experiment. The axes
    have the same (log-log scale) range.
    }
    \label{fig:gauss_mix_2}
\end{figure*}

@@

We benchmark with {\sc AustereMH(c)} and {\sc MHSubLhd}. We initialized {\sc
MHminibatch} and {\sc MHSubLhd} with $m=100$. For {\sc MHSubLhd}, we increase
sizes geometrically with $\gamma = 1.5$ and use parameters $p = 2, \delta =
0.01$.  All methods collect 5000 samples using a random walk proposer with
covariance matrix ${\rm diag}(0.15, 0.15)$, which means the M-H test is
responsible for shaping the sample distribution.

@@

Figure~\ref{fig:gauss_mix_2} shows that {\sc MHminibatch} dominates in terms of
speed and efficiency. The histograms of the (final) minibatch sizes used each
iteration show that our method consumes significantly less data; the
distribution is short-tailed and the mean is 210, more than an order of
magnitude better compared to the other two methods (averages are 15562 and
16857). Sizes correspond to the running times of the methods, excluding the
likelihood computation of all data points for {\sc MHSubLhd}, which would
drastically increase running time.

>>>>

% Daniel: moving this here so figures don't overflow to next pages. We can tune
% the positioning if needed.
\begin{figure*}[t]
    \centering
    %\includegraphics[width=0.9\linewidth]{posterior_of_gaussian.png}
    \includegraphics[width=1.0\linewidth]{gaussian_mixture_scatter_results_v8.png}
    \caption{
    The log posterior contours and scatter plots of sampled $\theta$ values
    using different methods. 
    }
    \label{fig:gauss_mix_1}
\end{figure*}
\begin{figure*}[t]
    \centering
    %\includegraphics[width=0.9\linewidth]{minibatch_size_gaussian.png}
    \includegraphics[width=0.9\linewidth]{gaussian_mixture_histogram_results_v8.png}
    \caption{
    Minibatch sizes used in Section~\ref{ssec:gaussians}'s experiment. The axes
    have the same (log-log scale) range.
    }
    \label{fig:gauss_mix_2}
\end{figure*}

@@

We benchmark with {\sc AustereMH(c)} and {\sc MHSubLhd}. We initialized {\sc
MHminibatch} and {\sc MHSubLhd} with $m=50$. For {\sc AustereMH(c)}, we set
the error bound $\epsilon$ to 0.005.  For {\sc MHSubLhd}, we increase
sizes geometrically with $\gamma = 1.5$ and use parameters $p = 2, \delta =
0.01$.  All methods collect 3000 samples using a random walk proposer with
covariance matrix ${\rm diag}(0.15, 0.15)$, which means the M-H test is
responsible for shaping the sample distribution.

@@

Figure~\ref{fig:gauss_mix_2} shows that {\sc MHminibatch} dominates in terms of
speed and efficiency. The histograms of the (final) minibatch sizes used each
iteration show that our method consumes significantly less data; the
distribution is short-tailed and the mean is 181, more than an order of
magnitude better compared to the other two methods (averages are 13511 and
73011). Sizes correspond to the running times of the methods, excluding the
likelihood computation of all data points for {\sc MHSubLhd}, which would
drastically increase running time.
